---
title: "Analysis: comparison of base R and ggplot"
output:
  html_document:
    highlight: espresso
---

# Loading packages and reading data

```{r}
library(tidyverse)
library(xtable)
library(devtools)
```

```{r}
summ_all <- read_csv("data/summ_all_FINAL.csv", guess_max = 1e6)
summ_comply <- read_csv("data/summ_comply_FINAL.csv", guess_max = 1e6)
sumtable1 <- read_csv("data/base_table_all_FINAL.csv", guess_max = 1e6)
sumtable2 <- read_csv("data/ggplot_table_all_FINAL.csv", guess_max = 1e6)
sumtable1_no_upload_rm <- read_csv("data/base_table_FINAL.csv", guess_max = 1e6)
sumtable2_no_upload_rm <- read_csv("data/ggplot_table_FINAL.csv", guess_max = 1e6)
base_annots <- read_csv("data/base_annots_FINAL.csv", guess_max = 1e6)
ggplot_annots <- read_csv("data/ggplot_annots_FINAL.csv", guess_max = 1e6)
base_annots$peer_submission_is_draft[is.na(base_annots$peer_submission_is_draft)] <- FALSE
ggplot_annots$peer_submission_is_draft[is.na(ggplot_annots$peer_submission_is_draft)] <- FALSE
```

# Analysis

Create shorter versions of the prompts.

```{r}
prompts <- tibble(
    prompt = unique(summ_all$prompt),
    short_prompt = c(
        "Legends and labels sufficient?",
        "Text and labels large enough?",
        "Understandable without caption?",
        "Did they upload a plot?",
        "Use full words vs. abbreviations?",
        "Clearly shows relationships?",
        "Is the plot visually pleasing?",
        "Clearly shows relationship?"
    )
)
```

Add an indicator to the annotation data frames for whether the observation should be kept (submission was reviewed or not a draft submission if not reviewed).

```{r}
base_annots <- base_annots %>%
    mutate(
        reviewed = deid_url %in% sumtable1$deid_url,
        keep = reviewed | (!reviewed & !peer_submission_is_draft)
    ) %>%
    select(-reviewed) %>%
    filter(keep)
ggplot_annots <- ggplot_annots %>%
    mutate(
        reviewed = deid_url %in% sumtable2$deid_url,
        keep = reviewed | (!reviewed & !peer_submission_is_draft)
    ) %>%
    select(-reviewed) %>%
    filter(keep)
```

## Sample sizes

How many students participated in the trial?

Count the number of unique JHU user IDs.

```{r}
sum(is.na(sumtable1$deid_jhu_user_id))
sum(is.na(sumtable2$deid_jhu_user_id))
sum(is.na(base_annots %>% pull(deid_jhu_user_id)))
sum(is.na(ggplot_annots %>% pull(deid_jhu_user_id)))

## Base R
setdiff(sumtable1$deid_jhu_user_id, NA) %>% length()
setdiff(base_annots$deid_jhu_user_id, NA) %>% length()
setdiff(c(sumtable1$deid_jhu_user_id, base_annots$deid_jhu_user_id), NA) %>% length()

## ggplot
setdiff(sumtable2$deid_jhu_user_id, NA) %>% length()
setdiff(ggplot_annots$deid_jhu_user_id, NA) %>% length()
setdiff(c(sumtable2$deid_jhu_user_id, ggplot_annots$deid_jhu_user_id), NA) %>% length()
```

How many plots were submitted?

```{r}
sum(is.na(base_annots$deid_url))
sum(is.na(ggplot_annots$deid_url))

urls_base_simple <- base_annots %>%
    filter(section=="simple") %>%
    pull(deid_url) %>%
    unique()
urls_base_complex <- base_annots %>%
    filter(section=="complex") %>%
    pull(deid_url) %>%
    unique()
length(urls_base_simple)
length(urls_base_complex)
length(urls_base_simple)+length(urls_base_complex)

urls_ggplot_simple <- ggplot_annots %>%
    filter(section=="simple") %>%
    pull(deid_url) %>%
    unique()
urls_ggplot_complex <- ggplot_annots %>%
    filter(section=="complex") %>%
    pull(deid_url) %>%
    unique()
length(urls_ggplot_simple)
length(urls_ggplot_complex)
length(urls_ggplot_simple)+length(urls_ggplot_complex)
```

How many of the submitted plots were reviewed? Answer: not all submitted plots underwent peer review.

```{r}
table(urls_base_simple %in% sumtable1_no_upload_rm$deid_url, useNA = "ifany")
table(urls_base_complex %in% sumtable1_no_upload_rm$deid_url, useNA = "ifany")

table(urls_ggplot_simple %in% sumtable2_no_upload_rm$deid_url, useNA = "ifany")
table(urls_ggplot_complex %in% sumtable2_no_upload_rm$deid_url, useNA = "ifany")
```


How many peer reviews are there?

```{r}
num_reviews_base_simple <- (sumtable1 %>% filter(section=="simple") %>% nrow())/7
num_reviews_base_complex <- (sumtable1 %>% filter(section=="complex") %>% nrow())/7
num_reviews_base_simple
num_reviews_base_complex

num_reviews_ggplot_simple <- (sumtable2 %>% filter(section=="simple") %>% nrow())/7
num_reviews_ggplot_complex <- (sumtable2 %>% filter(section=="complex") %>% nrow())/7
num_reviews_ggplot_simple
num_reviews_ggplot_complex
```

How many peer reviews were removed when removing reviews where upload="No"? How many plots does that correspond to?

```{r}
num_reviews_base_simple_subs <- (sumtable1_no_upload_rm %>% filter(section=="simple") %>% nrow())/7
num_reviews_base_complex_subs <- (sumtable1_no_upload_rm %>% filter(section=="complex") %>% nrow())/7
num_reviews_base_simple - num_reviews_base_simple_subs
num_reviews_base_complex - num_reviews_base_complex_subs
num_reviews_base_simple_subs
num_reviews_base_complex_subs

num_reviews_ggplot_simple_subs <- (sumtable2_no_upload_rm %>% filter(section=="simple") %>% nrow())/7
num_reviews_ggplot_complex_subs <- (sumtable2_no_upload_rm %>% filter(section=="complex") %>% nrow())/7
num_reviews_ggplot_simple - num_reviews_ggplot_simple_subs
num_reviews_ggplot_complex - num_reviews_ggplot_complex_subs
num_reviews_ggplot_simple_subs
num_reviews_ggplot_complex_subs
```

What is the distribution of the number of submissions reviewed by a single student?

```{r}
distribution_num_reviewed <- function(sumtable, what = c("deid_jhu_user_id", "deid_url")) {
    what <- match.arg(what)
    review_ids <- unique(sumtable$deid_peer_review_id)
    user_ids <- lapply(review_ids, function(id) {
        df_subs <- sumtable %>%
            filter(deid_peer_review_id==id)
        unique(df_subs[[what]])
    })
    cat("# unique IDs per review:\n")
    print(lengths(user_ids) %>% table())
    user_ids <- unlist(user_ids)
    cat("Total # unique IDs:\n")
    print(user_ids %>% unique() %>% length())
    num_reviewed <- table(user_ids)
    if (what=="deid_jhu_user_id") {
        thing <- "# submissions reviewed by a reviewer"
    } else if (what=="deid_url") {
        thing <- "# reviewers who reviewed a plot"
    }
    cat("Range, mean, median of", thing, ":\n")
    print(range(num_reviewed))
    print(mean(num_reviewed))
    print(median(num_reviewed))
    barplot(user_ids %>% table() %>% table())
}
distribution_num_reviewed(sumtable1_no_upload_rm, what = "deid_jhu_user_id")
distribution_num_reviewed(sumtable2_no_upload_rm, what = "deid_jhu_user_id")

distribution_num_reviewed(sumtable1, what = "deid_jhu_user_id")
distribution_num_reviewed(sumtable2, what = "deid_jhu_user_id")
```

Each plot was reviewed by how many students?

```{r}
distribution_num_reviewed(sumtable1_no_upload_rm, what = "deid_url")
distribution_num_reviewed(sumtable2_no_upload_rm, what = "deid_url")

distribution_num_reviewed(sumtable1, what = "deid_url")
distribution_num_reviewed(sumtable2, what = "deid_url")
```

## Compliance status

For how many URLs is correct_system TRUE? In other words, what fraction of submissions were made in the correct plotting system?

```{r}
count_compliance <- function(annots, plot_type = c("simple", "complex")) {
    plot_type <- match.arg(plot_type)
    annots %>%
        filter(keep, section==plot_type) %>%
        select(deid_url, correct_system) %>%
        unique() %>%
        count(correct_system)
}
comply_base_simple <- count_compliance(base_annots, plot_type = "simple")
comply_base_complex <- count_compliance(base_annots, plot_type = "complex")

comply_ggplot_simple <- count_compliance(ggplot_annots, plot_type = "simple")
comply_ggplot_complex <- count_compliance(ggplot_annots, plot_type = "complex")

df_comply <- data.frame(
    arm = rep(c("Base R", "ggplot2"), each = 2),
    plot = rep(c("simple", "complex"), 2),
    num_plots = c(
        sum(comply_base_simple$n),
        sum(comply_base_complex$n),
        sum(comply_ggplot_simple$n),
        sum(comply_ggplot_complex$n)
    ),
    num_annot = c(
        sum(comply_base_simple$n[!is.na(comply_base_simple$correct_system)]),
        sum(comply_base_complex$n[!is.na(comply_base_complex$correct_system)]),
        sum(comply_ggplot_simple$n[!is.na(comply_ggplot_simple$correct_system)]),
        sum(comply_ggplot_complex$n[!is.na(comply_ggplot_complex$correct_system)])
    )
)
num_compliant <- c(
    comply_base_simple %>% filter(correct_system) %>% pull(n),
    comply_base_complex %>% filter(correct_system) %>% pull(n),
    comply_ggplot_simple %>% filter(correct_system) %>% pull(n),
    comply_ggplot_complex %>% filter(correct_system) %>% pull(n)
)
perc_compliant <- paste0(round(num_compliant/df_comply$num_annot, 3)*100, "%")
df_comply$perc_compliant <- paste0(perc_compliant, " (", num_compliant, "/", df_comply$num_annot, ")")
colnames(df_comply) <- c("Arm", "Plot", "# plots", "# annotated", "% compliant")
print(xtable(df_comply), include.rownames = FALSE)

## 95% CIs for comparing compliance between arms
## Simple
prop.test(x = c(558, 357), n = c(561, 385))
0.9946524-0.9272727
## Complex
prop.test(x = c(582, 349), n = c(584, 399))
0.9965753-0.8746867
```

Go to each review and tabulate compliance for the simple plot and the complex plot.

```{r}
base_comply_sections <- sumtable1_no_upload_rm %>% 
    group_by(deid_peer_review_id, section) %>%
    summarize(
        urls = paste(unique(deid_url), collapse = ","),
        comply = paste(unique(correct_system), collapse = ",")
    )
base_comply_sections$comply[base_comply_sections$comply=="NA"] <- NA
ggplot_comply_sections <- sumtable2_no_upload_rm %>% 
    group_by(deid_peer_review_id, section) %>%
    summarize(
        urls = paste(unique(deid_url), collapse = ","),
        comply = paste(unique(correct_system), collapse = ",")
    )
ggplot_comply_sections$comply[ggplot_comply_sections$comply=="NA"] <- NA
base_comply_sections2 <- do.call(rbind, lapply(base_comply_sections$deid_peer_review_id, function(id) {
    df_subs <- base_comply_sections %>% filter(deid_peer_review_id==id)
    if (sum(df_subs$section=="simple")==0) {
        url_simple <- NA
        comply_simple <- NA
    } else {
        url_simple <- df_subs$urls[df_subs$section=="simple"]
        comply_simple <- df_subs$comply[df_subs$section=="simple"]
    }
    if (sum(df_subs$section=="complex")==0) {
        url_complex <- NA
        comply_complex <- NA
    } else {
        url_complex <- df_subs$urls[df_subs$section=="complex"]
        comply_complex <- df_subs$comply[df_subs$section=="complex"]
    }
    data.frame(
        url_simple = url_simple,
        url_complex = url_complex,
        comply_simple = comply_simple,
        comply_complex = comply_complex,
        stringsAsFactors = FALSE
    )
}))
ggplot_comply_sections2 <- do.call(rbind, lapply(ggplot_comply_sections$deid_peer_review_id, function(id) {
    df_subs <- ggplot_comply_sections %>% filter(deid_peer_review_id==id)
    if (sum(df_subs$section=="simple")==0) {
        url_simple <- NA
        comply_simple <- NA
    } else {
        url_simple <- df_subs$urls[df_subs$section=="simple"]
        comply_simple <- df_subs$comply[df_subs$section=="simple"]
    }
    if (sum(df_subs$section=="complex")==0) {
        url_complex <- NA
        comply_complex <- NA
    } else {
        url_complex <- df_subs$urls[df_subs$section=="complex"]
        comply_complex <- df_subs$comply[df_subs$section=="complex"]
    }
    data.frame(
        url_simple = url_simple,
        url_complex = url_complex,
        comply_simple = comply_simple,
        comply_complex = comply_complex,
        stringsAsFactors = FALSE
    )
}))
base_comply_sections2 <- unique(base_comply_sections2)
ggplot_comply_sections2 <- unique(ggplot_comply_sections2)

base_comply_sections_summ <- base_comply_sections2 %>%
    count(comply_simple, comply_complex) %>%
    arrange(desc(n))
ggplot_comply_sections_summ <- ggplot_comply_sections2 %>%
    count(comply_simple, comply_complex) %>%
    arrange(desc(n))

base_comply_sections_summ
ggplot_comply_sections_summ

319+25+17
515+2+1+1
```

## Overall summary tables

Make a table that has a row for every rubric question+response possible (excluding no's) and proportions for base R, ggplot2, and difference in proportions. CIs should be displayed too.

```{r}
make_results_table <- function(sum_tab) {
    prompts_ordered <- c(
        "Clearly shows",
        "visually pleasing",
        "caption",
        "Legends and labels",
        "Text and labels",
        "abbreviations"
            )
    do.call(rbind, lapply(c("simple", "complex"), function(sect) {
        do.call(rbind, lapply(prompts_ordered, function(p) {
            sub_tbl <- sum_tab %>%
                filter(short_prompt %>% str_detect(p)) %>%
                filter(section==sect)
            responses <- unique(sub_tbl$option)
            do.call(rbind, lapply(responses, function(resp) {
                sub_tbl2 <- sub_tbl %>% filter(option==resp)
                count_base <- sub_tbl2 %>% filter(arm=="base") %>% pull(count)
                tot_base <- sub_tbl2 %>% filter(arm=="base") %>% pull(total_reviews)
                count_gg <- sub_tbl2 %>% filter(arm=="ggplot") %>% pull(count)
                tot_gg <- sub_tbl2 %>% filter(arm=="ggplot") %>% pull(total_reviews)
                ptest_res <- prop.test(x = c(count_base, count_gg), n = c(tot_base, tot_gg))
                # is_signif <- length(unique(sign(ptest_res$conf.int)))==1
                stopifnot(length(unique(sub_tbl2$short_prompt))==1)
                prop_diff <- diff(ptest_res$estimate) %>% round(3)
                prop_diff <- paste0(prop_diff*100, "%")
                ci_prop_diff <- -rev(ptest_res$conf.int) %>% round(3)
                ci_prop_diff <- paste0("(", paste0(ci_prop_diff*100, "%", collapse = ", "), ")")
                # if (is_signif) {
                #     ci_prop_diff <- paste0(ci_prop_diff, "*")
                # }
                data.frame(
                    "Plot" = sect,
                    "Prompt" = sub_tbl2$short_prompt[1],
                    "Response" = resp,
                    "Base R" = paste0(round(ptest_res$estimate[1], 3)*100, "% (", count_base, "/", tot_base, ")"),
                    "ggplot2" = paste0(round(ptest_res$estimate[2], 3)*100, "% (", count_gg, "/", tot_gg, ")"),
                    "ggplot2 - base R" = paste(prop_diff, ci_prop_diff)
                )
            }))
        }))
    }))
}

summ_all_clean <- summ_all %>%
    filter(option != "No") %>%
    left_join(prompts)
results_table <- make_results_table(summ_all_clean)
rownames(results_table) <- NULL
colnames(results_table) <- c("Plot", "Prompt", "Response", "Base R", "ggplot2", "ggplot2 - base R")
print(xtable(results_table), include.rownames = FALSE)

summ_comply_clean <- summ_comply %>%
    filter(option != "No") %>%
    left_join(prompts)
results_table_comply <- make_results_table(summ_comply_clean)
rownames(results_table_comply) <- NULL
colnames(results_table_comply) <- c("Plot", "Prompt", "Response", "Base R", "ggplot2", "ggplot2 - base R")
print(xtable(results_table_comply), include.rownames = FALSE)
```

## Analysis of manual annotations

Organize truly base R and truly ggplot2 submissions.

```{r}
base_annots_unique <- base_annots %>%
    filter(keep) %>%
    select(deid_url, correct_system:fixed_axis_scales) %>%
    unique()
noncompliers_base <- base_annots_unique %>%
    filter(!correct_system)
base_annots_unique <- base_annots_unique %>%
    filter(correct_system)

ggplot_annots_unique <- ggplot_annots %>%
    filter(keep) %>%
    select(deid_url, correct_system:fixed_axis_scales) %>%
    unique()
noncompliers_gg <- ggplot_annots_unique %>%
    filter(!correct_system)
ggplot_annots_unique <- ggplot_annots_unique %>%
    filter(correct_system)

## Put the truly base R submissions together
base_annots_unique <- rbind(base_annots_unique, noncompliers_gg)
## Put the truly ggplot2 submissions together
ggplot_annots_unique <- rbind(ggplot_annots_unique, noncompliers_base)
```

For every plot feature annotated (except for "correct system"), calculate `P(perceived as clear | plot feature present)` compared to `P(perceived as clear | plot feature absent)`.

```{r}
identical(colnames(base_annots_unique), colnames(ggplot_annots_unique))
plot_features_all <- setdiff(colnames(base_annots_unique), c("deid_url", "correct_system", "notes", "section"))
plot_features_simple <- plot_features_all[1:14]

## Base R
as_treated_base <- rbind(
    sumtable1_no_upload_rm %>% filter(correct_system),
    sumtable2_no_upload_rm %>% filter(!correct_system)
) %>%
    rename(
        prompt = peer_assignment_review_schema_part_prompt,
        option = peer_assignment_review_schema_part_option_text
    ) %>%
    mutate(arm = "base")

## ggplot2
as_treated_gg <- rbind(
    sumtable2_no_upload_rm %>% filter(correct_system),
    sumtable1_no_upload_rm %>% filter(!correct_system)
) %>%
    rename(
        prompt = peer_assignment_review_schema_part_prompt,
        option = peer_assignment_review_schema_part_option_text
    ) %>%
    mutate(arm = "ggplot")

lapply(plot_features_all, function(feat) {
    base_subs <- as_treated_base %>%
        filter(
            str_detect(prompt, "clearly show the relationship") | str_detect(prompt, "without a figure caption") | str_detect(prompt, "legends and labels sufficient")
        )
    base_subs <- base_subs[,c("prompt", "option", "section", feat)]
    feat <- sym(feat)
    df_sampsize <- base_subs %>%
        group_by(prompt, section) %>%
        summarize(tot_base = n())
    res <- base_subs %>%
        count(prompt, option, section, !!feat) %>%
        left_join(df_sampsize) %>%
        filter(option != "No") %>%
        arrange(section, prompt, !!feat)
})

identical(colnames(as_treated_base), colnames(as_treated_gg))
as_treated_all_subs <- rbind(as_treated_base, as_treated_gg) %>%
    select(-peer_submission_is_draft, -notes, -starts_with("deid_")) %>%
    filter(
        str_detect(prompt, "clearly show the relationship") | str_detect(prompt, "without a figure caption") | str_detect(prompt, "legends and labels sufficient")
    ) %>%
    mutate(
        both_axis_lab = has_axis_lab=="xy",
        non_default_axis_lab = !default_axis_lab,
        good_plot_sizing = !poor_plot_sizing,
        no_lab_cut_off = !lab_cut_off,
        med_code_clear = !med_code_number_only,
        fixed_axis_scales = fixed_axis_scales=="xy"
    ) %>%
    select(-c(has_axis_lab, default_axis_lab, poor_plot_sizing, lab_cut_off, med_code_number_only))
as_treated_all_subs <- as_treated_all_subs %>%
    gather(key = "plot_feature", value = "plot_feature_value", -c(prompt, option, section, arm))
df_sampsize <- count(as_treated_all_subs, arm, section, plot_feature, prompt, plot_feature_value, name = "total")
plot_features_all <- c("is_scatterplot", "shows_points", "both_axis_lab", "non_default_axis_lab", "has_units_lab", "has_caption_title", "has_trendline", "has_guideline", "lines_labeled", "good_plot_sizing", "legend_present", "no_lab_cut_off", "med_code_clear", "panel_label_complete", "fixed_axis_scales")
plot_features_labels <- c("Is scatterplot", "Shows points", "Has x & y axis labels", "Non-default axis labels", "Has units", "Has informative title", "Has trend line", "Has guide line", "Lines labeled", "Good plot sizing", "Legend present", "No labels cut off", "Medical code is clear", "Panel labels are complete", "Fixed x & y axis scales")
res <- as_treated_all_subs %>%
    count(arm, section, plot_feature, prompt, option, plot_feature_value) %>%
    left_join(df_sampsize) %>%
    filter(option != "No", plot_feature %in% plot_features_all, !is.na(plot_feature_value)) %>%
    left_join(prompts) %>%
    mutate(
        frac = n/total,
        plot_feature = factor(plot_feature, levels = rev(plot_features_all), labels = rev(plot_features_labels)),
        section = factor(section, levels = c("simple", "complex")),
        arm = factor(arm, levels = c("base", "ggplot"), labels = c("Base R", "ggplot2")),
        short_prompt = str_wrap(short_prompt, width = 20),
        x_pos_sampsize = ifelse(plot_feature_value, -0.25, -0.7)
    )

## Specific data for explanation in text
res %>%
    filter(arm=="Base R", section=="simple", plot_feature=="Is scatterplot") %>%
    select(-arm, -section, -plot_feature, -x_pos_sampsize)

p <- ggplot(res, aes(x = frac, y = plot_feature, color = plot_feature_value)) +
    geom_point() +
    geom_text(aes(x = x_pos_sampsize, y = plot_feature, label = total, color = plot_feature_value), size = 3, show.legend = FALSE, hjust = 0) +
    facet_grid(arm ~ section+short_prompt) +
    theme_bw() +
    labs(x = "Fraction of student reviews indicating \"Yes, the plot is clear.\"", y = "Plot feature") +
    guides(color = guide_legend(title = "Plot feature present?")) +
    theme(legend.position = "bottom") +
    coord_cartesian(xlim = c(-0.7,1)) +
    scale_x_continuous(breaks = c(0.2, 0.6, 1))
pdf("figures/plot_features_clarity.pdf", width = 10, height = 6)
print(p)
dev.off()
```

Count how often the annotated features occur in base R and ggplot2.

```{r}
base_annots_unique <- base_annots_unique %>%
    mutate(
        both_axis_lab = has_axis_lab=="xy",
        non_default_axis_lab = !default_axis_lab,
        good_plot_sizing = !poor_plot_sizing,
        no_lab_cut_off = !lab_cut_off,
        med_code_clear = !med_code_number_only,
        fixed_axis_scales = fixed_axis_scales=="xy"
    ) %>%
    select(-c(has_axis_lab, default_axis_lab, poor_plot_sizing, lab_cut_off, med_code_number_only))
ggplot_annots_unique <- ggplot_annots_unique %>%
    mutate(
        both_axis_lab = has_axis_lab=="xy",
        non_default_axis_lab = !default_axis_lab,
        good_plot_sizing = !poor_plot_sizing,
        no_lab_cut_off = !lab_cut_off,
        med_code_clear = !med_code_number_only,
        fixed_axis_scales = fixed_axis_scales=="xy"
    ) %>%
    select(-c(has_axis_lab, default_axis_lab, poor_plot_sizing, lab_cut_off, med_code_number_only))

feature_freqs <- do.call(rbind, lapply(plot_features_all, function(feat) {
    feat_char <- feat
    feat <- sym(feat)
    base_sampsize <- base_annots_unique %>%
        filter(!is.na(!!feat)) %>%
        count(section, name = "tot_base")
    freq_base <- count(base_annots_unique, section, !!feat, name = "num_base") %>%
        left_join(base_sampsize) %>%
        mutate(
            frac_base = num_base/tot_base,
            frac_base = paste0(round(frac_base, 3)*100, "% (", num_base, "/", tot_base, ")")
        ) %>%
        filter(!is.na(!!feat)) %>%
        filter(!!feat)
    gg_sampsize <- ggplot_annots_unique %>%
        filter(!is.na(!!feat)) %>%
        count(section, name = "tot_gg")
    freq_gg <- count(ggplot_annots_unique, section, !!feat, name = "num_gg") %>%
        left_join(gg_sampsize) %>%
        mutate(
            frac_gg = num_gg/tot_gg,
            frac_gg = paste0(round(frac_gg, 3)*100, "% (", num_gg, "/", tot_gg, ")")
        ) %>%
        filter(!is.na(!!feat)) %>%
        filter(!!feat)
    full_join(freq_base, freq_gg) %>%
        select(-(!!feat)) %>%
        select(-starts_with("num"), -starts_with("tot")) %>%
        mutate(feature = feat_char, feature = factor(feature, levels = plot_features_all, labels = plot_features_labels)) %>%
        select(feature, section, frac_base, frac_gg)
}))
colnames(feature_freqs) <- c("Plot feature", "Plot type", "Base R", "ggplot2")

feature_freqs_feats <- feature_freqs[1] %>% unique()
feature_freqs_simple <- feature_freqs %>%
    filter(`Plot type`=="simple") %>%
    select(-`Plot type`, `Base R simple` = `Base R`, `ggplot2 simple` = `ggplot2`)
feature_freqs_complex <- feature_freqs %>%
    filter(`Plot type`=="complex") %>%
    select(-`Plot type`, `Base R complex` = `Base R`, `ggplot2 complex` = `ggplot2`)
feature_freqs2 <- left_join(feature_freqs_feats, feature_freqs_simple) %>% left_join(feature_freqs_complex)

print(xtable(feature_freqs2), include.rownames = FALSE)
```

### Types of complex plots

Count plot types.

```{r}
base_plot_type_counts <- base_annots_unique %>%
    filter(!is.na(num_panels)) %>%
    group_by(num_panels, other_visual_grouping) %>%
    summarize(total_base = n()) %>%
    arrange(total_base)
ggplot_plot_type_counts <- ggplot_annots_unique %>%
    filter(!is.na(num_panels)) %>%
    group_by(num_panels, other_visual_grouping) %>%
    summarize(total_gg = n()) %>%
    arrange(total_gg)

dplyr::intersect(base_plot_type_counts[,1:2], ggplot_plot_type_counts[,1:2])
dplyr::setdiff(base_plot_type_counts[,1:2], ggplot_plot_type_counts[,1:2])
dplyr::setdiff(ggplot_plot_type_counts[,1:2], base_plot_type_counts[,1:2])
```

Compare percentages of plots of different types between the arms.

```{r}
all_plot_type_counts <- full_join(base_plot_type_counts, ggplot_plot_type_counts)
n_base <- sum(base_plot_type_counts$total_base)
n_gg <- sum(ggplot_plot_type_counts$total_gg)

all_plot_type_counts <- all_plot_type_counts %>%
    mutate(frac_base = total_base/n_base, frac_gg = total_gg/n_gg)
all_plot_type_counts <- all_plot_type_counts %>%
    mutate(plot_type = case_when(
            num_panels==36 & other_visual_grouping==FALSE ~ "36 panels",
            num_panels==12 & other_visual_grouping==FALSE ~ "12 panels, no color",
            num_panels==12 & other_visual_grouping==TRUE ~ "12 panels, color",
            num_panels==6 & other_visual_grouping==FALSE ~ "6 panels, no color",
            num_panels==6 & other_visual_grouping==TRUE ~ "6 panels, color",
            num_panels==2 & other_visual_grouping==TRUE ~ "2 panels, color"
        )
    )

plot_types <- c("36 panels", "12 panels, no color", "12 panels, color", "6 panels, no color", "6 panels, color", "2 panels, color")
tab_results_complex_types <- do.call(rbind, lapply(plot_types, function(ptype) {
    df_subs <- all_plot_type_counts %>%
        filter(plot_type==ptype)
    df_subs$total_base[is.na(df_subs$total_base)] <- 0
    df_subs$total_gg[is.na(df_subs$total_gg)] <- 0
    tot_base <- df_subs$total_base
    tot_gg <- df_subs$total_gg
    ptest_res <- prop.test(x = c(tot_base, tot_gg), n = c(n_base, n_gg))
    prop_diff <- diff(ptest_res$estimate) %>% round(3)
    prop_diff <- paste0(prop_diff*100, "%")
    ci_prop_diff <- -rev(ptest_res$conf.int) %>% round(3)
    ci_prop_diff <- paste0("(", paste0(ci_prop_diff*100, "%", collapse = ", "), ")")
    data.frame(
        "Plot type" = ptype,
        "Base R" = paste0(round(ptest_res$estimate[1], 3)*100, "% (", tot_base, "/", n_base, ")"),
        "ggplot2" = paste0(round(ptest_res$estimate[2], 3)*100, "% (", tot_gg, "/", n_gg, ")"),
        "ggplot2 - base R" = paste(prop_diff, ci_prop_diff)
    )
}))
colnames(tab_results_complex_types) <- c("Plot type", "Base R", "ggplot2", "ggplot2 - base R")
rownames(tab_results_complex_types) <- NULL
tab_results_complex_types

print(xtable(tab_results_complex_types), include.rownames = FALSE)
```

What are the peer review rubric responses for these different plot types? That is, are certain plot types more clear or more visually pleasing than others?

```{r}
summarize_reviews_by_plottype <- function(data) {
    data %>%
        mutate(plot_type = case_when(
                num_panels==36 ~ "36 panels",
                num_panels==12 & other_visual_grouping==FALSE ~ "12 panels, no color",
                num_panels==12 & other_visual_grouping==TRUE ~ "12 panels, color",
                num_panels==6 & other_visual_grouping==FALSE ~ "6 panels, no color",
                num_panels==6 & other_visual_grouping==TRUE ~ "6 panels, color",
                num_panels==2 & other_visual_grouping==TRUE ~ "2 panels, color"
            )
        ) %>%
        mutate(plot_type = factor(plot_type, levels = c("36 panels", "12 panels, no color", "12 panels, color", "6 panels, no color", "6 panels, color", "2 panels, color"))) %>%
        arrange(plot_type) %>%
        rename(prompt = peer_assignment_review_schema_part_prompt, option = peer_assignment_review_schema_part_option_text) %>%
        left_join(prompts) %>%
        filter(!is.na(plot_type), str_detect(prompt, "clearly")) %>%
        group_by(prompt, option, plot_type) %>%
        summarize(count = n()) %>%
        group_by(prompt, plot_type) %>%
        mutate(tot_reviews = sum(count)) %>%
        ungroup() %>%
        filter(option=="Yes") %>%
        mutate(frac = count/tot_reviews) %>%
        select(plot_type:frac) %>%
        mutate(results = paste0(round(frac, 3)*100, "% (", count, "/", tot_reviews, ")"))
}

## Base R
as_treated_base <- rbind(
    sumtable1_no_upload_rm %>% filter(correct_system),
    sumtable2_no_upload_rm %>% filter(!correct_system)
)
summ_plottypes_base <- summarize_reviews_by_plottype(as_treated_base)

## ggplot2
as_treated_gg <- rbind(
    sumtable2_no_upload_rm %>% filter(correct_system),
    sumtable1_no_upload_rm %>% filter(!correct_system)
)
summ_plottypes_gg <- summarize_reviews_by_plottype(as_treated_gg)

summ_plottypes_base <- summ_plottypes_base %>% select(plot_type, count_base = count, tot_reviews_base = tot_reviews, results_base = results)
summ_plottypes_gg <- summ_plottypes_gg %>% select(plot_type, count_gg = count, tot_reviews_gg = tot_reviews, results_gg = results)

df_clarity_plot_types <- full_join(summ_plottypes_base, summ_plottypes_gg)
df_clarity_plot_types <- df_clarity_plot_types %>%
    mutate(
        diff = (count_gg/tot_reviews_gg) - (count_base/tot_reviews_base),
        diff = paste0(round(diff, 3)*100, "%")
    )
cis <- sapply(seq_len(nrow(df_clarity_plot_types)), function(r) {
    x_base <- df_clarity_plot_types$count_base[r]
    x_gg <- df_clarity_plot_types$count_gg[r]
    n_base <- df_clarity_plot_types$tot_reviews_base[r]
    n_gg <- df_clarity_plot_types$tot_reviews_gg[r]
    ci <- prop.test(x = c(x_gg, x_base), n = c(n_gg, n_base))$conf.int
    paste(paste0(round(ci, 3)*100, "%"), collapse = ", ")
})
df_clarity_plot_types <- df_clarity_plot_types %>%
    mutate(ci = cis, diff = paste0(diff, " (", ci, ")")) %>%
    select(plot_type, results_base, results_gg, diff)
colnames(df_clarity_plot_types) <- c("Plot type", "Base R", "ggplot2", "ggplot2 - Base R")
print(xtable(df_clarity_plot_types), include.rownames = FALSE)
```


# Session info

```{r}
session_info()
```
